\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{SMDE Assignment}

\author{\IEEEauthorblockN{1\textsuperscript{st} Carles Matoses}
\IEEEauthorblockA{carles.matoses@estudiantat.upc.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Ignasi Granell}
\IEEEauthorblockA{ignasi.granell@estudiantat.upc.edu}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Isabel Castañeda}
\IEEEauthorblockA{isabel.castaneda@estudiantat.upc.edu}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section*{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits. 

\section{Problem description}
% add the issues you detect. 
% In the Marathon, are enough resources for the runners? (WC, water sources, meals…), there are some unexpected queues, what about make the race on august?
We are provided with three marathon results, from a Keggle dataset, on the years 2015, 2016 and 2017. The data is structured in a way that we have the runners' information, the time they took to get to interest points and the time they took to finish the race. Some of the most relevant variables we are provided are: the age, the genre and the city of origin. We believe this characteristics have a direct impact on the performance of the runners.

By reading the paper \cite{b8}

\section{System description, introduction}
\section{Model specification}
\subsection{Systemic Structural, Systemic Data and Simplifying Hypotheses}
\section{Coding}
\subsection{Data}
\section{Definition of the experimental framework}
\section{Model validation}
\section{Results/Conclusions}

\begin{thebibliography}{00}
% \bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
% \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
% \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
% \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
% \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
% \bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
% \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\bibitem{b8} B. Knechtle, C. McGrath, O. Goncerz, E. Villiger, P. T. Nikolaidis, T. Marcin, and C. V. Sousa, ``The Role of Environmental Conditions on Master Marathon Running Performance in 1,280,557 Finishers the ‘New York City Marathon’ From 1970 to 2019,'' Frontiers in Physiology, vol. 12, 2021. [Online]. Available: https://www.frontiersin.org/journals/physiology/articles/10.3389/fphys.2021.665761. DOI: 10.3389/fphys.2021.665761. ISSN: 1664-042X.


\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}
